\bf Hierarchical Forecasts Reconciliation

### 2019-07-02 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Tidying up of everything but ooblique projections

    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \todo{citations}, before elaborating on some of the limitations of this understanding.  A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables. We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$. The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.  The hierarchical structure of the data implies that

    \begin{equation}
    \bm{y}_t = \bm{Sb}_t,
    \end{equation}
    where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints, holds for all $t$.

@@

	While such a definition is completely serviceable, it obscures the full generality of many methodologies developed in the literature on so-called hierarchical time series.  In fact, to apply concepts such as coherence and reconciliation, the data only require two important characteristics; the first is that they are multivariate, the second is that they adhere to linear constraints.  Below we redefine the concepts of coherence and hierarchical time series using a geometric interpretation, before turning our attention to forecast reconciliation in Section~\ref{sec:Reconciliation}.

@@

@@

     Also notable by its absence in the above definition is any reference to {\em aggregation}.  As the literature has shown, the linear constraints need not be aggregation constraints at all. For example \todo{find reference} consider weighted sums, while \todo{include Li and Tang reference} consider an example where one variable is the difference of two other variables.

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.   In fact, the term {\em hierarchical} is misleading since the literature has covered instances that cannot easily be depicted as hierarchies as in Figure~\ref{fig:basichier}.  These include \todo{include references}.  Furthermore, although the definition makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$, made using information up to and including time $t$. Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
	\end{definition}

@@

	\begin{definition}[Reconciled forecasts]\label{def:reconpoint}
		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.  The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$ iff
		\begin{equation}
		\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)\,.
		\end{equation}
	\end{definition}

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  One way to achieve this is with a matrix $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases), where $\bm{G}$ is an $(n-m)\times n$ matrix.  This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix.  We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.  This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011} where the connection between OLS and orthogonal projection should be clear.

@@

	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.  A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible given that $\tilde{\bm{y}}\in\mathfrak{s}$.  In this way reconciliation via orthogonal projection does not lead to large adjustments of the base forecasts.

@@

	Consider the Euclidean distance between a forecast and the target, which is equivalent to the root total squared error. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

	\begin{theo}[Distance reducing property]
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$. Therefore,
		\begin{align}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{align}
		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
		\begin{equation*}
		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{equation*}
	\end{proof}
	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.

@@

	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.  In this schematic, the coherent subspace is depicted as a black arrow.  The base forecast $\hat{\bm{y}}$ is shown as a blue dot.  Since it is incoherent it does not lie of $\mathfrak{s}$.  Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.  Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.

@@

    The theorem is in some ways perhaps more powerful than perhaps previously understood.  The theorem is often stated in terms of expectations\todo{check other proofs}.  However, the distance reducing property result is stronger than that since it will hold for any realisation and any forecast.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.

    However, in other ways, the theorem is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts both for all realisations and in expectation, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

@@

	\section{The issue of bias}

	A sensible property is that reconciliation should not change base forecasts that are already coherent.  That is 
	\begin{equation}	
	\label{eq:propcohnochange}
	\tilde{\bm{y}}_{t+h|t}=\bm{SG}\hat{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h|t}\mbox{ iff }
	\hat{\bm{y}}_{t+h|t}\in\mathfrak{s}\,.
	\end{equation}

	Using geometric intuition, it should be clear that the property in Equation~\ref{eq:propcohnochange} will hold when $\bm{SG}$ is a projection matrix \todo{perhaps find a reference - it is so fundamental that is is on wikipedia and wolfram mathworld}.  This also implies that the the property in Equation~\ref{eq:propcohnochange} does not hold for arbitrary $\bm{G}$.  For this reason it is often assumed that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Enforcing these assumptions are equivalent to assuming that  $\bm{SG}$ is a projection matrix.\todo{perhaps elaborate in a proof in appendix}

	The property that projections map all vectors in the coherent subspace onto themselves is useful in proving the unbiasedness preserving property of reconciliation, previously proven by\todo{reference Shanika and maybe van Erven Culigari}.  Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.  Our point forecast is an estimate of this quantity that is random due to sampling variation.  The point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.

@@

	\begin{figure}[!b]
		\centering
		\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/Schem_3D}
		}
		\caption{$\mathfrak{L}$ is a linear subspace of the coherent subspace $\mathfrak{s}$. If $s\circ g$ is a projection not onto $\mathfrak{s}$ but onto $\mathfrak{L}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bar{\bm{\mu}} \in \mathfrak{L}$.}\label{fig:Schematic_3D}
	\end{figure}

>>>>

    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{Wickramasuriya2017}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.  A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables. We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$. The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.  The hierarchical structure of the data implies that the following holds for all $t$

    \begin{equation}
    \bm{y}_t = \bm{Sb}_t,
    \end{equation}
    where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.

@@

	While such a definition is completely serviceable, it obscures the full generality of the literature on so-called hierarchical time series.  In fact, concepts such as coherence and reconciliation, defined in full below, only require the data to have two important characteristics; the first is that they are multivariate, the second is that they adhere to linear constraints.

@@

	The property that data adhere to some linear constraints is referred to as {\em coherence}.  We now provide definitions aimed at providing geometric intuition of hierarchical time series.

@@

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot easily be depicted in a similar fashion to Figure~\ref{fig:basichier} and or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although the Definition~\ref{def:cohspace} makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a vector of point forecasts of all series in the hierarchy at time $t+h$, made using information up to and including time $t$. Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
	\end{definition}

@@

	\begin{definition}[Reconciled forecasts]\label{def:reconpoint}
		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.  The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ is said to ``reconcile'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
	\end{definition}

	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.  One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (with some authors using $\bm{P}$ used in place of $\bm{G}$).  This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.  In general a projection matrix has the idemoptence property, i.e. $\bm{SG}^2=\bm{SG}$.  However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped onto itself by that projection. \todo{perhaps find a reference - it is so fundamental that is is on wikipedia and wolfram mathworld}  In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.

	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.  This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011} where the connection between OLS and orthogonal projection should be clear.

@@

	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.  A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible while still ensuring that $\tilde{\bm{y}}\in\mathfrak{s}$.  In this sense reconciliation via orthogonal projection does leads to the smallest possible adjustments of the base forecasts.

@@

	Consider the Euclidean distance between a forecast and the target. This is equivalent to the root of the sum of squared errors over the entire hierarchy. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$. Therefore,
		\begin{align}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{align}
		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
		\begin{equation*}
		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{equation*}
	\end{proof}
	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.

@@

	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.  In this schematic, the coherent subspace is depicted as a black arrow.  The base forecast $\hat{\bm{y}}$ is shown as a blue dot.  Since it is incoherent it does not lie in $\mathfrak{s}$.  Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.  Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.

@@

    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.  It is often stated in terms of expectations\todo{check other proofs}.  However, the distance reducing property result is even stronger since it will hold for any realisation and any forecast.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.

    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts both for all realisations and in expectation, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

@@

	\section{Bias in forecast reconciliation}

	Before turning our attention to the issue of bias itself it is important to state a sensible property that any reconciliation method should have.  That is if base forecasts are already coherent then reconciliation should not change the forecast.  As stated in Section~\ref{sec:Reconciliation}, this property holds when $\bm{SG}$ is a projection matrix.  This implies for arbitrary $\bm{G}$, reconciliation may in fact change an already coherent forecast.

	The property that projections map all vectors in the coherent subspace onto themselves is useful in proving the unbiasedness preserving property of reconciliation \todo{reference Shanika and maybe van Erven Culigari}.  Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.

	Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.  Our point forecast can be thought of as an estimate of this quantity.  The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness refers.  More concretely, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.

@@

	\begin{figure}[H]
		\centering
		\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/Schem_3D}
		}
		\caption{$\mathfrak{L}$ is a linear subspace of the coherent subspace $\mathfrak{s}$. If $s\circ g$ is a projection not onto $\mathfrak{s}$ but onto $\mathfrak{L}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bar{\bm{\mu}} \in \mathfrak{L}$.}\label{fig:Schematic_3D}
	\end{figure}

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.  \todo{perhaps elaborate in a proof in appendix}  When the problem is viewed through the prism of imposing a constraint $\bm{GS}=\bm{I}$ to ensure unbiasedness is preserved, one may be tempted to deal with biased forecasts by selecting $\bm{G}$ is an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  Our own solution to dealing with biased forecasts is discussed in detail in the next section.
